A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-10 manuscript.Rmd
revamp simulation still WIP

A cornerstone of scientific progress is the possibility to critically assess the validity of peer scientists’ scientific conclusions.
Scientific claims should not be credible because of their originators' authority but by the transparency and replicability of their supporting evidence [@aac4716].
Here, *replicability* refers to the degree to which original studies and their derivatives yield consistent results.In other words, a succesful replication study finds a consistent effect with an original study in a new sample of data.
Enabling the assessment of scientific conclusions requires a systematic and rigorous approach to research.
Researchers across various fields have identified a *crisis* of non-replicability of findings [e.g. @aac4716]- <!--citation needed, e.g. [@aac4716]-->

<!-- define replicability and then... 
 define reproducibility -->
Even worse, researchers might often not even be able to achieve reproducibility---defined as the ability to obtain identical results from the *same* data with the *same* computer code.
Over the past decades, computational statistical methods have radically changed the ability of researchers from all disciplines to process and analyze data with complex statistical models.
With these advances came challenges that contribute to broader concerns of irreproducibility in the published literature, among them the lack of exact and unambiguous documentation of computational methods and each computational step taken.
With computationally intensive data analyses, access to the steps taken to process data and generate findings is as important as access to the data themselves.
Only with access to both data and procedures can we guarantee full computational reproducibility, meaning that the creations emanating from a given data analysis (a statistical result or an entire manuscript describing the results) can be exactly reproduced at any time in the future, by any person, and on any computer.
Only if both the data and code are shared, can we obtain a reproducible scientific product, facilitating assessment of its validity and later reuse.

@@

1.	Multiple inconsistent versions of code and data; for example, the dataset has changed over time because outliers were removed at a later stage, or the code has changed because a bug was removed at some point in time;
2.	Copy-and-paste errors; for example, results are manually copied from a computing environment into a text processor, causing inconsistencies between the reported result and the reproduced result;
.3.	Ambiguous order of code execution; for example, with multiple data and code files, it may be unclear which scripts should be executed in what order;
4.	Broken dependencies; for example, a given analysis depends on a software package that might not be available on a different computer or no longer exists.

@@

This tutorial guides the reader through each step of an open research project with an emphasis on guaranteeing reproducibility from the very first step on.
We start by sketching an initial idea in a repository shared with colleagues that potentially collaborate only remotely.
We continue with the creation of a concrete data analysis plan, which ideally is already implemented in code, and a dynamic report document that can be preregistered.
Once the empirical data has been collected, the results can be calculated and appear directly in the dynamically generated document, where ideally only the discussion section needs to be added before the whole archive can be permanently stored as a fully reproducible digital artifact using a unique DOI in a persistent location.

@@

# Organizing Files

@@

## Dynamic Documents

@@

It is common practice to have a target all, that encompasses all important files of the project as the first target.
If you do not specify a target, Make defaults to the first target, which is usually `all`.
`repro` reminds you of that and suggests which file you might want to add to the target `all`.
After you have done so, you can then run in the terminal:

@@

```bash
# this should be run in the terminal
make DOCKER=TRUE
```

You can also manually edit the `Dockerfile` by amending the file `.repro/Dockerfile_manuel` to install software beyond R packages.
Remember to run `repro::automate()` after you made edits to `.repro/Dockerfile_manuel`.
We recommend @wiebelsLeveragingContainersReproducible2021 as a starting point for researcher who want to better understand how they can employ Docker for research.

@@

@@

<!-- Hands-on: check changed hash -->
A prerequisite to reproducibility is the availability of code and data.
We use containers to guarantee that all code components are available and work as expected.
Ideally, all data is also stored in the repository.
In practice, however, there are various reasons, which may prohibit you from making your data available, for example legal or regulatory or privacy concerns.
You may find yourself in a situation where you can make the data only available on request.
A major threat to reproducibility is that the data has changed in the meantime or multiple versions are circulating and it is not exactly clear what version was used originally.
To at least check that the data was not changed, we suggest to provide a so called "hash", which is a cryptographic fingerprint.
If the data changes, so does its fingerprint or hash.
The user can therefore compare if the data they have received is the same that was used in the original publication, as long as the original publication does contain the hash of the data.

@@

@@

Here, we provided a step-by-step tutorial with what we think are best practices for creating a fully reproducible repository for data analysis projects that center on the statistical programming language R.
The workflow avoids common threats to reproducibility, such as copy-and-paste errors, missing files, missing software dependencies, or side-effects through changing dependent software packages, changes in the programming language, or even at the level of the operating system itself.
However, the workflow as proposed by @Peikert2019 requires mastering up to four different software tools and their specification languages, which are typically not taught in the curriculum of social and behavioral sciences but rather belong to computer science and software development.
Currently, this is a serious obstacle in adopting the workflow for researchers who strive for reproducibility but have little training in computer science and software development.
The repro package, which we introduced here, supports scholars in creating reproducible workflows.
It abstracts tedious and error-prone tasks such as the creation of a Makefile or the specification of a container.
By extending the YAML specification that is used for storing meta information in R Markdown files, which are becoming increasingly popular among R users, repro helps users to implement @Peikert2019's workflow with minimal effort.
Most importantly, repro is implemented such that the package itself is not needed to reproduce a workflow that was generated according to the workflow.
Importantly, this means that users that adopt the workflow do not have to rely on the future availability and maintenance of the repro package.

>>>>

A cornerstone of scientific progress is the possibility to critically assess the validity of peer scientists’ scientific conclusions.
Scientific claims should not be credible because of their originators' authority but by the transparency and replicability of their supporting evidence [@aac4716].
Here, *replicability* refers to the degree to which original studies and their derivatives yield consistent results.
In other words, a successful replication study finds a consistent effect with an original study in a new sample of data.
Enabling the assessment of scientific conclusions requires a systematic and rigorous approach to research.
Researchers across various fields have identified a *crisis* of non-replicability of findings [e.g. @aac4716]. <!--citation needed, e.g. [@aac4716]-->

<!-- define replicability and then... 
 define reproducibility -->
Even worse, researchers might often not even be able to achieve reproducibility---defined as the ability to obtain identical results from the *same* data with the *same* computer code.
Over the past decades, computational statistical methods have radically changed the ability of researchers from all disciplines to process and analyze data with complex statistical models.
With these advances came challenges that contribute to broader concerns of irreproducibility in the published literature, among them the lack of exact and unambiguous documentation of computational methods and each computational step taken.
With computationally intensive data analyses, access to the steps taken to process data and generate findings is as important as access to the data themselves [@vanlissa2020worcs].
Only with access to both data and procedures can we guarantee full computational reproducibility, meaning that the creations emanating from a given data analysis (a statistical result or an entire manuscript describing the results) can be exactly reproduced at any time in the future, by any person, and on any computer.
With computationally intensive data analyses, access to the steps taken to process data and generate findings is as important as access to the data themselves [@vanlissa2020worcs].

@@

1.	Multiple inconsistent versions of code and data; for example, the dataset has changed over time because outliers were removed at a later stage, or the code has changed because a bug was removed at some point in time;
2.	Copy-and-paste errors; for example, results are manually copied from a computing environment into a text processor, causing inconsistencies between the reported result and the reproduced result;
3.	Ambiguous order of code execution; for example, with multiple data and code files, it may be unclear which scripts should be executed in what order;
4.	Broken dependencies; for example, a given analysis depends on a software package that might not be available on a different computer or no longer exists.

@@

This tutorial guides the reader through each step of an open research project with an emphasis on guaranteeing reproducibility from the very first step on.
This paper was designed to help researchers to practically apply the TOP guidelines [except for number 8. which does not apply to single research projects; @nosekPromotingOpenResearch2015; @vanlissa2020worcs].
We start by sketching an initial idea in a repository shared with colleagues that potentially collaborate only remotely.
We continue with the creation of a concrete data analysis plan, which ideally is already implemented in code, and a dynamic report document that can be preregistered.
Once the empirical data has been collected, the results can be calculated and appear directly in the dynamically generated document, where ideally only the discussion section needs to be added before the whole archive can be permanently stored as a fully reproducible digital artifact using a unique DOI in a persistent location.

@@

# Planning Phase

@@

## Markdown

@@

It is common practice to have a target all, that encompasses all important files of the project as the first target.
If you do not specify a target, Make defaults to the first target, which is usually `all`.
`repro` reminds you of that and suggests which file you might want to add to the target `all`.
You can generally change the `Makefile` anyway you want, e.g. to add targets which are not supported by `repro`.
After you have done so, you can then run in the terminal:

@@

```bash
# this should be run in the terminal
make DOCKER=TRUE
```
The function `automate()` combines `automate_docker()` & `automate_make()`.

You can also manually edit the `Dockerfile` by amending the file `.repro/Dockerfile_manual` to install software beyond R packages.
Remember to run `repro::automate()` after you made edits to `.repro/Dockerfile_manual`.
We recomend @wiebelsLeveragingContainersReproducible2021 as a starting point for researcher who want to better understand how they can employ Docker for research.

@@

Because you probably want to reproduce your own project each time something changes, you will often want to reproduce evertyhting.
The `repro`-package contains a function designed for that purpose:

```{r}
repro::rerun()
```

This function  automatically figures out how to reproduce a project  and also recognizes other employed reproducibility tools (like `renv` and `singularity`), but can of course only guess the appropriate way to reproduce a project.

@@

<!-- Hands-on: check changed hash -->
A prerequisite to reproducibility is the availability of code and data.
We use containers to guarantee that all code components are available and work as expected.
Ideally, all data is also stored in the repository [for a more comprehensive argument for publishing data see @vanlissa2020worcs], but this is not always feasible.
Sometimes it is just the required storage capacity that exceeds what Git can handle (Git gets slow around more than 100mb).
In such case we strongly recommend using [DataLad [@DataladDatalad2021]](http://handbook.datalad.org/en/latest/)[^datalad] or the below procedure to guarantee that the data has not changed.
In practice, however, there are various reasons, which may prohibit you from making your data publicly available, for example legal or regulatory or privacy concerns.
You may find yourself in a situation where you can make the data only available on request.
A major threat to reproducibility is that the data has changed in the meantime or multiple versions are circulating and it is not exactly clear what version was used originally.
To at least check that the data was not changed, we suggest to provide a so called "hash", which is a cryptographic fingerprint.
If the data changes, so does its fingerprint or hash.
The user can therefore compare if the data they have received is the same that was used in the original publication, as long as the original publication does contain the hash of the data.

@@

[^datalad]: http://handbook.datalad.org/en/latest/

@@

Here, we provided a step-by-step tutorial with what we think are best practices for creating a fully reproducible repository for data analysis projects that center on the statistical programming language R.
The workflow avoids common threats to reproducibility, such as copy-and-paste errors, missing files, missing software dependencies, or side-effects through changing dependent software packages, changes in the programming language, or even at the level of the operating system itself.
However, the workflow as proposed by @Peikert2019 requires mastering up to four different software tools and their specification languages, which are typically not taught in the curriculum of social and behavioral sciences but rather belong to computer science and software development.
Currently, this is a serious obstacle in adopting the workflow for researchers who strive for reproducibility but have little training in computer science and software development.
The repro package, which we introduced here, supports scholars in creating reproducible workflows.
It abstracts tedious and error-prone tasks such as the creation of a Makefile or the specification of a container.
By extending the YAML specification that is used for storing meta information in R Markdown files, which are becoming increasingly popular among R users, repro helps users to implement @Peikert2019's workflow with minimal effort.
Most importantly, `repro`-is implemented such that the package itself is not needed to reproduce a workflow that was generated according to the workflow.
Importantly, this means that users that adopt the workflow do not have to rely on the future availability and maintenance of the `repro`-package.
